\section{参考文献}
[1]Berkdemir, Cüneyt, and Sedat Özsoy. ‘An Investigation on the Temperature Dependence of the Relative Population Inversion and the Gain in EDFAs by the Modified Rate Equations’. Optics Communications 254, no. 4–6 (October 2005): 248–55.\\


[2]Buscaino, Brandon, Mian Zhang, Marko Loncar, and Joseph M. Kahn. ‘Design of Efficient Resonator-Enhanced Electro-Optic Frequency Comb Generators’. Journal of Lightwave Technology 38, no. 6 (15 March 2020): 1400–1413.\\


[3]Carmon, Tal, Lan Yang, and Kerry J. Vahala. ‘Dynamical Thermal Behavior and Thermal Self-Stability of Microcavities’. Optics Express 12, no. 20 (4 October 2004): 4742.\\


[4]Del’Haye, P., T. Herr, E. Gavartin, M. L. Gorodetsky, R. Holzwarth, and T. J. Kippenberg. ‘Octave Spanning Tunable Frequency Comb from a Microresonator’. Physical Review Letters 107, no. 6 (1 August 2011): 063901.\\


[5]Del’Haye, P., A. Schliesser, O. Arcizet, T. Wilken, R. Holzwarth, and T. J. Kippenberg. ‘Optical Frequency Comb Generation from a Monolithic Microresonator’. Nature 450, no. 7173 (December 2007): 1214–17. \\


[6]Diddams, Scott A., Kerry Vahala, and Thomas Udem. ‘Optical Frequency Combs: Coherently Uniting the Electromagnetic Spectrum’. Science 369, no. 6501 (17 July 2020): eaay3676. \\


[7]Englebert, Nicolas, Carlos Mas Arabí, Pedro Parra-Rivas, Simon-Pierre Gorza, and François Leo. ‘Temporal Solitons in a Coherently Driven Active Resonator’. Nature Photonics 15, no. 7 (July 2021): 536–41. \\


[8]Guo, H., M. Karpov, E. Lucas, A. Kordts, M.H.P. Pfeiffer, V. Brasch, G. Lihachev, V.E. Lobanov, M.L. Gorodetsky, and T.J. Kippenberg. ‘Universal Dynamics and Deterministic Switching of Dissipative Kerr Solitons in Optical Microresonators’. Nature Physics 13, no. 1 (January 2017): 94–102. \\


[9]He, Yang, Qi-Fan Yang, Jingwei Ling, Rui Luo, Hanxiao Liang, Mingxiao Li, Boqiang Shen, Heming Wang, Kerry Vahala, and Qiang Lin. ‘Self-Starting Bi-Chromatic LiNbO3 Soliton Microcomb’. Optica 6, no. 9 (20 September 2019): 1138–44. \\


[10]Herr, T., V. Brasch, J. D. Jost, C. Y. Wang, N. M. Kondratiev, M. L. Gorodetsky, and T. J. Kippenberg. ‘Temporal Solitons in Optical Microresonators’. Nature Photonics 8, no. 2 (February 2014): 145–52. \\


[11]Herr, T., K. Hartinger, J. Riemensberger, C. Y. Wang, E. Gavartin, R. Holzwarth, M. L. Gorodetsky, and T. J. Kippenberg. ‘Universal Formation Dynamics and Noise of Kerr-Frequency Combs in Microresonators’. Nature Photonics 6, no. 7 (July 2012): 480–87. \\


[12]Kippenberg, T. J., R. Holzwarth, and S. A. Diddams. ‘Microresonator-Based Optical Frequency Combs’. Science 332, no. 6029 (29 April 2011): 555–59. \\


[13]Liu, YiAn, XiongShuo Yan, JiangWei Wu, Bing Zhu, YuPing Chen, and XianFeng Chen. ‘On-Chip Erbium-Doped Lithium Niobate Microcavity Laser’. Science China Physics, Mechanics and Astronomy 64, no. 3 (March 2021): 234262. \\


[14]Vahala, Kerry J. ‘Optical Microcavities’. Nature 424, no. 6950 (August 2003): 839–46. \\


[15]Yi, Xu, Qi-Fan Yang, Ki Youl Yang, and Kerry Vahala. ‘Active Capture and Stabilization of Temporal Solitons in Microresonators’. Optics Letters 41, no. 9 (1 May 2016): 2037–40. \\


[16]Zhang, Mian, Brandon Buscaino, Cheng Wang, Amirhassan Shams-Ansari, Christian Reimer, Rongrong Zhu, Joseph M. Kahn, and Marko Lončar. ‘Broadband Electro-Optic Frequency Comb Generation in a Lithium Niobate Microring Resonator’. Nature 568, no. 7752 (April 2019): 373–77. \\


[17]Zhu, Di, Linbo Shao, Mengjie Yu, Rebecca Cheng, Boris Desiatov, C. J. Xin, Yaowen Hu, et al. ‘Integrated Photonics on Thin-Film Lithium Niobate’. Advances in Optics and Photonics 13, no. 2 (30 June 2021): 242–352. \\
